---
title: "Visualizing Data"
subtitle: "75694189 16257626 13341225 49442423"
author: "Chen Wang, Junke Wang, Zhuozhi Xiong, Titas Dutta"
date: "due:Oct 9, 2019 at the end of discussion"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r message = FALSE}
library(tidyverse)
library(fivethirtyeight)
library(titanic)
```


## Slide 9 Plot

Text:

1. Survived

2. Survived is on the x-axis 

3. Bar plot

Code:

```{r}
titanic_train %>% 
  ggplot(aes(x = Survived)) +
  geom_bar()
```

\pagebreak



## Slide 10 Plot

Text:

1. Fare

2. Fare is on the x-axis

3. Histogram

Code:

```{r}
titanic_train %>% 
  
  ggplot(aes(x=Fare)) +
  geom_histogram(binwidth=40)
```

\pagebreak

## Slide 11 plot

Text:

1. Fare

2. Fare is on the x-axis

3. Histogram


Code:

```{r}
titanic_train %>% 
  
  ggplot(aes(x=Fare)) +
  geom_histogram(bins = 40)
```

\pagebreak

## Slide 13 plot

Text:

1. Pclass and Fare

2. Pclass on x-axis, Fare on y-axis

3. Boxplot

```{r}
titanic_train %>% 
  ggplot(aes(x=factor(Pclass), y= Fare)) +
  geom_boxplot() +
  xlab("Pclass")
```

\pagebreak

## Slide 15 plot

Text:

1. Age and Fare

2. Age is on x-axis and Fare is on y-axis

3. Scatter-plot

Code:

```{r}
titanic_train %>% 
  ggplot(aes(x=Age, y= Fare)) +
  geom_point(na.rm=TRUE)
```

No real relationship between Age and Fare

\pagebreak

## Slide 21 plot

Text:

1. Pclass, Survived

2. Pclass on the x-axis, Survived stacked 

3. Stacked bar plot


Code:

```{r}
titanic_train %>% 
  ggplot(aes(x=factor(Pclass), fill=Survived)) +
  geom_bar(aes(fill=factor(Survived))) +
  xlab("Pclass")
```

\pagebreak

## Slide 22 plot


Text:

1. domgross, binary(FAIL/PASS)

2. domgross on the x-axis, binary stacked

3. Stacked histogram

Code:

```{r}
bechdel %>% 
  ggplot(aes(x=domgross, fill = binary))+
  geom_histogram(aes(fill=binary),bins = 80,na.rm=TRUE) +
  scale_fill_manual(values = c("blue", "magenta"))
```

